%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\topmargin = -45pt
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[finnish]{babel}
\usepackage{hyperref}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.5in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%   NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Pentti Sunila} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}%\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

% address 
% \moveleft.5\hoffset\centerline{7329 Marc Drive}
% \moveleft.5\hoffset\centerline{Falls Church, VA 22042}


%\moveleft.5\hoffset\centerline{pentti.sunila@helsinki.fi}
%\moveleft.5\hoffset\centerline{\url{https://github.com/gingerdeer}}
%\moveleft.5\hoffset\centerline{\url{https://gingerdeer.github.io}}
%\moveleft.5\hoffset\centerline{+358 40 562 5105}
%\moveleft.5\hoffset\centerline{github.com/supercowz}
% \moveleft.5\hoffset\centerline{\hyperref[www.linkedin.com/in/pentti-sunila-a967a1123]{Linked in}}


%----------------------------------------------------------------------------------------

\begin{resume}

%
% Top Matter
%

%----------------------------------------------------------------------------------------
%   PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}
  
 \textbf{Topcoder}\\
 %{\sl Community Marketing \& Program Manager} \hfill 2021 - \\
 {\sl Community Manager} \hfill 2021 - 2023 \\
 \begin{itemize}
 	\item Community Strategy
 	\item Competitive Programming \& Development
 	\item Rapid Development Match competition format; coordination and problem writing
 	\item (Mathematical) Puzzle competition format; creation, coordination and problem writing
 	\item Europe region
 	\item Scheduling, approvals, comms, events, webinars
 	\item Competition management
 	\item Program management
 	\item QA projects
 	\item Advisor role for internal projects and development activities
 	\item Crowd For Good Cancer Research project, advisor role
 \end{itemize}
 {\sl Developer Edgenet Evangelist} \hfill 2021 
 \begin{itemize} \itemsep -2pt % Reduce space between items
 	\item Developer Advocacy for a client partnership, Competitive Programming \& \\ Development, Community Member
 	\item 5G, Edge Computing, Machine Learning, Image Processing
 	\item Community management, Communication \& representation, Technical development work, Guidance \& educational work, content, Client work
 \end{itemize}

\textbf{University of Helsinki}\\
{\sl Course Instructor / Teaching Assistant} \hfill 2021 - 2022  \\
\begin{itemize}
	\item Introduction to Statistics and R Programming I
	\item Introduction to Statistics and R Programming II
	\item Bayesian Inference
	\item Geometry
	\item Mathematics of Machine Learning
\end{itemize}
  
\textbf{IBM Global Services}\\
{\sl Trainee, Cloud App Migration Services} \hfill 2018 - 2020
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Client work for a public sector client.
\item Keywords: cloud transformation, automated testing, information security, multi-vendor environment; Kubernetes, Openshift, Enterprise Java, Microservices, Robot framework, Watson technology
\end{itemize}

\addvspace{-7pt}
\textbf{TV Tools}\\
{\sl Software Developer} \hfill 2018
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Worked as a software developer on various front and back-end solutions related to media delivery, asset and log management, and monitoring.
\item Worked with: Docker, Elasticsearch, Grafana, Low level binary protocols, hardware network interfaces, C\#, Ruby, React.js, Lawo VSM
\end{itemize}

\addvspace{-7pt}
\textbf{Nixu Corporation}\\
{\sl Summer Trainee, Situational Awareness} \hfill 2016
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Evaluated various security software solutions.
\item Worked with:  IBM QRadar, ELK Stack, LogPoint, AWS, RHEL, CentOS, Debian, Windows Server, Python, Bash, Ruby, Perl, Metasploit
\item Participated in an informal information security contest (CTF), Cyberlympics 2016, as captain of Nixu summer intern team ``Fuzzbuzz''  
\end{itemize}

\addvspace{-7pt}
\textbf{Hyrylän yläaste}\\
{\sl Substitute teacher} \hfill 2015
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Taught maths, chemistry, and programming to grades 7 - 9
\end{itemize}
\addvspace{-7pt}
  
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\newpage

\moveleft.5\hoffset\centerline{\large\bf Pentti Sunila} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}%\smallskip % Horizontal line after name; adjust line

\addvspace{-7pt}


\section{EDUCATION}

\textbf{University of Helsinki} \hfill 2017 - present\\
Master degree, Mathematics. Minor studies in Finno-ugric linguistics.
\begin{itemize} \itemsep -2pt
	\item Completed credits: 300+ total, graduating as M.Sc. in 2022. Plan to start PhD in 2022.
	\item Masters' thesis title: Sobolev gradients and partial differential equations, with applications in image processing
	\item Masters' thesis specialization on gradient methods in function spaces + applications (Optimization, Inverse Problems, Image \& Signal processing, PDE)
	\item Courses of note: Inverse Problems, Statistical Inference with R, Mathematics of infectious diseases, Intro. Wavelet Analysis
	\item Additional cultural \& linguistic studies, especially on finno-ugristics
	\item Course Instructor / Teaching Assistant for various courses
	\item Faculty council student representative (Faculty of Science)
\end{itemize}

\textbf{University of Helsinki} \hfill 2013 - 2017\\
Bachelor's degree, Mathematics. Minor subjects statistics \& Hungarian.
\begin{itemize} \itemsep -2pt
\item My bachelor's thesis was on the mathematical methods involved in X-Ray tomographic reconstruction (Inverse Problems)
\item Additional cultural \& linguistic studies, especially on finno-ugristics
\end{itemize}

\addvspace{-7pt}
\textbf{Tikkurilan lukio} \hfill 2010 - 2013\\
Graduated in 2013 with a bilingual IB Diploma.
\begin{itemize} \itemsep -2pt
\item I performed volunteer service at Heureka Science Centre as part of the CAS (Creativity, Action, Service) program.
\item I wrote my Extended Essay on the construction of real numbers from the rationals.
\item My Higher Level subjects were Finnish A, Mathematics, and Chemistry; Standard Level subjects were English A, Philosophy, and Physics. 
\end{itemize}

%\newpage


\section{SKILLS \& INTERESTS}
\begin{itemize} \itemsep -2pt
\item Languages: Native Finnish, CEFR C2 English (fluent), B2 Hungarian and Swedish, A2 Mandarin Chinese (HSK 3-4). Various other language / linguistic studies.
\item Active self study: for example, I have completed and audited several free courses on the Coursera online platform, including:
  \begin{itemize} \itemsep -2pt
  \item Machine Learning
  \item Social Network Analysis
  \item Advanced Competitive Strategy
  \item International Leadership and Organizational Behaviour
  \end{itemize}
\item \href{https://www.youracclaim.com/users/pentti-sunila/badges}{Some issued verified badges} on Acclaim platform.
\item Completed the CMX Academy Community MBA certificate course.
\item Topcoder community member since 2013.
\item Arts \& culture interests, hobbies.
\item Competitive programming \& CTF hobbyist participant.
\begin{itemize}
	\item \href{https://www.codingame.com/profile/e3a213a1df3e0d739af5ddb7dbfe73a07564915}{Penatrix} on CodinGame
	\item \href{https://www.hackerrank.com/_Pena}{\_Pena} on HackerRank
\end{itemize}
\item Folk \& Electronic musician (hobbyist).
\begin{itemize}
	\item \href{https://open.spotify.com/artist/4e6oG8yxaiw4UHudKs86G0}{GIDE on Spotify}
\end{itemize}
\item Member of the Finno-Ugrian Society of Finland.
\item Discord moderator of Topcoder community.
\item \href{https://github.com/gingerdeer}{GitHub page.}
\end{itemize}


% ----------------------------------------------------------------------------------------

\end{resume}
\end{document}
